Should geophysicists use gravity anomaly or gravity disturbance?

### 2018-05-16 manuscript/letter.tex
Use the vector symbol to make things clearer
It's very hard to see the bold gamma. I added the `\vec` command to draw
the little vector arrow to make things cleared. Kept the bold, like what
was used for the unit vectors.
I made the `\versor` and `\vector` commands to make it easier to control
the formatting for all the text.

@@

\begin{equation}
    \hat{\mitbf{u}} =
    \begin{bmatrix}
        \cos\varphi \, \cos\lambda \\
        \cos\varphi \, \sin\lambda \\
        \sin\varphi
    \end{bmatrix}
    \hat{\mitbf{v}} =
        \begin{bmatrix}
        -\sin\varphi \, \cos\lambda \\
        -\sin\varphi \, \sin\lambda \\
        \cos\varphi
    \end{bmatrix}
    \hat{\mitbf{w}} =
    \begin{bmatrix}
        -\sin\lambda \\
        \cos\lambda \\
        0
    \end{bmatrix} .
    \label{eq:unit-vectors}
\end{equation}

@@

The third is the Topocentric Cartesian System (TCS),
which is commonly used in local or regional scale geophysical studies.
The origin of the TCS is located at a point $P$,
axes $x$ and $y$ are parallel to
the unit vectors $\hat{\mitbf{v}}$ and $\hat{\mitbf{w}}$
(eq. \ref{eq:unit-vectors}), respectively,
and the $z$-axis is opposite to the unit vector $\hat{\mitbf{u}}$
(Fig. \ref{fig:TCS}).

@@

Let $\mitbf{\gamma}_{P}$ and $\mitbf{g}_{P}$ and be, respectively,
the \textit{normal gravity vector} and the Earth's \textit{gravity vector}
(corrected from non-gravitational effects due to vehicle
motion and time variations such as Earth tides and instrumental drift),
both located at a point $P$.
In this case, the gravity vector $\mitbf{g}_{P}$ is the
gradient of the scalar \textit{gravity potential},
which is the sum of a gravitational potential and a centrifugal potential.
Similarly, the normal gravity vector $\mitbf{\gamma}_{P}$ is the
gradient of the scalar \textit{normal potential},
which is also the sum of a gravitational and a centrifugal potential.
By definition, the centrifugal part of
the normal potential and the gravity potential are equal.

The difference between $\mitbf{g}_{P}$ and $\mitbf{\gamma}_{P}$,
which we emphasize are located at the same point $P$,
is the \textit{gravity disturbance vector} (Fig. \ref{fig:surfaces}):

\begin{equation}
\delta \mitbf{g}_{P} =
\mitbf{g}_{P} - \mitbf{\gamma}_{P} \: .
\label{eq:gravity-disturbance-vector}
\end{equation}

Because the centrifugal parts of both the normal gravity vector
and the Earth's gravity vector are equal,
the gravity disturbance vector $\delta \mitbf{g}_{P}$
represents a purely gravitational effect.
As a consequence of the superposition principal \citep{blakely1996},
this effect is caused by contrasts between
the internal density distributions
of the actual Earth and the normal Earth.
In applied geophysics, these density differences are generally called
\textit{anomalous masses} \citep[e.g.,][]{hammer1945,lafehr1965},
\textit{density anomalies} \citep[e.g.,][]{forsberg1984},
or \textit{gravity sources} \citep[e.g.,][]{blakely1996}.
Here, we opted for using the last term.

The difference between the magnitudes of gravity vector
$g_{P} = \| \mitbf{g}_{P} \|$ and the normal gravity vector
$\gamma_{P} = \| \mitbf{\gamma}_{P} \|$, at the
same point $P$, is called \textit{gravity disturbance}
\citep{heiskanen-moritz1967, hofmann-wellenhof-moritz2005}
and can be represented as follows:

@@

Notice that the gravity disturbance $\delta g_{P}$ is not equivalent
to the magnitude of the gravity disturbance vector
$\delta \mitbf{g}_{P}$ \citep{barthelmes2013, sanso_sideris2013}.

On the other hand, the \textit{gravity anomaly vector} at $P$
is the difference between the gravity
vector at a point $Q^{\prime}$ on the Geoid (a particular
equipotential surface of the gravity potential) and the normal
gravity vector at a point $Q$ on the ellipsoid surface, both at the
same geodetic latitude and longitude (Fig. \ref{fig:surfaces}) as in
\begin{equation}
\Delta \mitbf{g}_{P} = \mitbf{g}_{Q^{\prime}} - \mitbf{\gamma}_{Q} .
\label{eq:gravity-anomaly-vector}
\end{equation}
Similarly to the gravity disturbance expression (eq.
\ref{eq:gravity-disturbance}), the gravity anomaly is given by
\begin{equation}
\Delta g_{P} = g_{Q^{\prime}} - \gamma_{Q} ,
\label{eq:gravity-anomaly}
\end{equation}
where $g_{Q^{\prime} } = \| \mitbf{g}_{Q^{\prime}} \|$ is
the magnitude of the gravity vector $\mitbf{g}_{Q}$ on the Geoid,
at $Q^{\prime}$, and $\gamma_{Q} = \| \mitbf{\gamma}_{Q} \|$ is the
magnitude of the normal gravity vector $\mitbf{\gamma}_{Q}$
on the reference ellipsoid, at the point $Q$ (Fig. \ref{fig:surfaces}).
As properly pointed out by \citet{barthelmes2013} the gravity anomaly,
by definition, depends on
longitude and latitude only and is not a function of height.
Because the gravity is on the Geoid and the normal gravity
is on reference ellipsoid, the gravity anomaly $\Delta g_{P}$
(eq. \ref{eq:gravity-anomaly}) is not a purely gravitational effect
due to the gravity sources, but rather a combination of gravitational
and centrifugal effects. Consequently, its upward continuation,
for example, could not be rigorously done.

@@

From eq. \ref{eq:gravity-disturbance-vector}, the gravity vector $\mitbf{g}_{i}$, at a point
$(x_{i}, y_{i}, z_{i})$ in the TCS (Fig. \ref{fig:TCS}a), can be represented by:
\begin{equation}
\mitbf{g}_{i} = \mitbf{\gamma}_{i} + \delta \mitbf{g}_{i} \: ,
\label{eq:gravity-vector-TCS}
\end{equation}
where $\mitbf{\gamma}_{i}$ and $\delta \mitbf{g}_{i}$
are, respectively, the normal gravity vector and the
gravity disturbance vector produced by the anomalous
masses at the point $(x_{i}, y_{i}, z_{i})$.

The gravity $g_{i}$ can be approximated by a first order Taylor's
expansion as follows \citep{sanso_sideris2013}:
\begin{equation}
g_{i} \approx \gamma_{i} +
\hat{\mitbf{\gamma}}_{i}^{\top} \delta \mitbf{g}_{i} \: ,
\label{eq:gobs-approx}
\end{equation}
where $^{\top}$ denotes transposition,
$\hat{\mitbf{\gamma}}_{i} = -\hat{\mitbf{u}}_{i}$ is a unit
vector with the same direction as the normal gravity vector
$\mitbf{\gamma}_{i}$ at the point $(x_{i}, y_{i}, z_{i})$, in the
topocentric Cartesian coordinate system (Fig. \ref{fig:TCS}a), and
$\hat{\mitbf{u}}_{i}$ is the unit vector $\hat{\mitbf{u}}$
(eq. \ref{eq:unit-vectors}) evaluated at the corresponding
point $(h_{i}, \varphi_{i}, \lambda_{i})$ in the
GGS (Fig. \ref{fig:GCS-GGS}).
This approximation can be made because, fortunately,
the condition $\gamma_{i} \gg \| \delta \mathbf{g}_{i} \|$
is met at all points located above or on the Earth's surface.
This approximation is known in geodesy \citep[e.g.,][]{sanso_sideris2013}
and a similar approximation is largely used in applied geophysics
for representing total-field anomalies \citep[e.g.,][]{blakely1996}.
Notice that, in local- or regional-gravity studies, the unit
vector $\hat{\mitbf{\gamma}}_{i}$ (eq. \ref{eq:gobs-approx})
may be considered constant throughout the study area and
parallel to the $z$ axis of the TCS (Fig. \ref{fig:TCS}a).
By using the approximation defined in eq.
\ref{eq:gobs-approx}, the gravity disturbance
(eq. \ref{eq:gravity-disturbance}) can be rewritten as
follows
\begin{equation}
\delta g_{i} \approx \hat{\mitbf{\gamma}}_{P}^{\top} \delta \mitbf{g}_{i} \: ,
\label{eq:gravity-disturbance-approx-TCS}
\end{equation}
where $\hat{\mitbf{\gamma}}_{P}$ represents the unit vector with
the same direction as the normal gravity vector $\mitbf{\gamma}_{P}$
at the origin $P$ of the TCS (Fig. \ref{fig:TCS}a).
This equation shows that the gravity disturbance $\delta g_{i}$ (eq. \ref{eq:gravity-disturbance}) is different from the magnitude
of the gravity disturbance vector $\delta \mitbf{g}_{i}$
produced by the gravity sources. Rather, it represents the
component of $\delta \mitbf{g}_{i}$ on the direction of the normal
gravity vector \citep{hofmann-wellenhof-moritz2005, sanso_sideris2013}.

@@

\begin{figure}
%    \vspace{5.5cm}
    \includegraphics{figures/cartesian-geodetic-systems.png}
    \caption{Schematic representation of the Geocentric Cartesian System (GCS) and the Geocentric Geodetic System (GGS). The GCS has the $Z$-axis coincident with the mean Earth's rotational axis,
    the $X$-axis pointing to the Greenwich meridian and the $Y$-axis
    directed so as to obtain a right-handed system. The GGS is      defined by an oblate ellipsoid with semi-minor axis $b$,
    coincident with the $Z$-axis of GCS, and a semi-major
    axis $a$. In this coordinate system, the position of a point is
    determined by the geometric height $h$, geodetic latitude
    $\varphi$ and longitude $\lambda$.
    The Earth's center of mass is represented
    by $O$, $P$ represents a point $(h_{P}, \varphi_{P}, \lambda_{P})$ and $P^{\prime}$ its projection onto the plane $XY$
    (Equatorial plane). The plane containing $O$, $P$ and
    $P^{\prime}$ is represented in gray in (a) and (b).
    The unit vectors $\hat{\mitbf{u}}_{P}$, $\hat{\mitbf{v}}_{P}$ and
    $\hat{\mitbf{w}}_{P}$ define three mutually orthogonal
    directions at $P$ (eq. \ref{eq:unit-vectors}).
    In (b), $Q$ represents a point $(h_{Q}, \varphi_{Q}, \lambda_{Q})$,
    which is the projection of $P$ onto the reference ellipsoid, at
    the same latitude and longitude ($\varphi_{Q} = \varphi_{P}$ and $\lambda_{Q} = \lambda_{P}$).}
  \label{fig:GCS-GGS}
\end{figure}

\begin{figure}
    \includegraphics{figures/local-system.png}
    \caption{(a) Schematic representation of a topocentric Cartesian
    coordinate system (TCS) with origin at a point $P$. The axes $x$
    and $y$ are parallel to the unit vectors $\hat{\mitbf{v}}_{P}$
    and $\hat{\mitbf{w}}_{P}$ (eq. \ref{eq:unit-vectors} and
    Fig. \ref{fig:GCS-GGS}), respectively. On the other hand, the $z$ axis is opposite to the unit vector $\hat{\mitbf{u}}_{P}$ (eq.
    \ref{eq:unit-vectors} and Fig. \ref{fig:GCS-GGS}) and points downward. The gray plane is the same shown in Fig. \ref{fig:GCS-GGS}.
    (b) Schematic representation of the gravity vector
    $\mitbf{g}_{P}$, normal gravity vector $\mitbf{\gamma}_{P}$,
    gravity disturbance vector $\delta \mitbf{g}_{P}$
    (eq. \ref{eq:gravity-disturbance-vector}) and unit vector
    $\hat{\mitbf{u}}_{P}$ (eq. \ref{eq:unit-vectors}) at a point
    $P$.}
  \label{fig:TCS}
\end{figure}

\begin{figure}
    \includegraphics{figures/surfaces.png}
    \caption{Schematic representation of the gravity vector
        $\mitbf{g}_{P}$, normal gravity vector $\mitbf{\gamma}_{P}$,
        gravity disturbance vector $\delta \mitbf{g}_{P}$
        (eq. \ref{eq:gravity-disturbance-vector}), unit vector
        $\hat{\mitbf{u}}_{P}$ (eq. \ref{eq:unit-vectors}) at a point $P$
        on the surface of the Earth, gravity vector $\mitbf{g}_{Q^{\prime}}$
        at a point $Q^{\prime}$ on the Geoid, normal gravity vector
        $\mitbf{\gamma}_{Q}$ at a point $Q$ on the reference ellipsoid,
        geometric height $h$, orthometric height $H$ and geoidal undulation
        $N$ \citep{heiskanen-moritz1967}.
        The dashed line passing through
        $Q$, $Q^{\prime}$ and $P$ is normal to the
        surface of the reference ellipsoid at $Q$. This figure
        shows a commonly used approximation in which the ellipsoid
        surface and the Geoid are represented as parallel surfaces,
        so that $h \approx H + N$.}
  \label{fig:surfaces}
\end{figure}

>>>>

\newcommand{\versor}[1]{\hat{\mathbf{#1}}}
\renewcommand{\vector}[1]{\vec{\mathbf{#1}}}

@@

\begin{equation}
    \versor{u} =
    \begin{bmatrix}
        \cos\varphi \, \cos\lambda \\
        \cos\varphi \, \sin\lambda \\
        \sin\varphi
    \end{bmatrix}
    \versor{v} =
        \begin{bmatrix}
        -\sin\varphi \, \cos\lambda \\
        -\sin\varphi \, \sin\lambda \\
        \cos\varphi
    \end{bmatrix}
    \versor{w} =
    \begin{bmatrix}
        -\sin\lambda \\
        \cos\lambda \\
        0
    \end{bmatrix} .
    \label{eq:unit-vectors}
\end{equation}

@@

The third is the Topocentric Cartesian System (TCS),
which is commonly used in local or regional scale geophysical studies.
The origin of the TCS is located at a point $P$,
axes $x$ and $y$ are parallel to
the unit vectors $\versor{v}$ and $\versor{w}$
(eq. \ref{eq:unit-vectors}), respectively,
and the $z$-axis is opposite to the unit vector $\versor{u}$
(Fig. \ref{fig:TCS}).

@@

Let $\vector{\gamma}_{P}$ and $\vector{g}_{P}$ and be, respectively,
the \textit{normal gravity vector} and the Earth's \textit{gravity vector}
(corrected from non-gravitational effects due to vehicle
motion and time variations such as Earth tides and instrumental drift),
both located at a point $P$.
In this case, the gravity vector $\vector{g}_{P}$ is the
gradient of the scalar \textit{gravity potential},
which is the sum of a gravitational potential and a centrifugal potential.
Similarly, the normal gravity vector $\vector{\gamma}_{P}$ is the
gradient of the scalar \textit{normal potential},
which is also the sum of a gravitational and a centrifugal potential.
By definition, the centrifugal part of
the normal potential and the gravity potential are equal.

The difference between $\vector{g}_{P}$ and $\vector{\gamma}_{P}$,
which we emphasize are located at the same point $P$,
is the \textit{gravity disturbance vector} (Fig. \ref{fig:surfaces}):

\begin{equation}
\delta \vector{g}_{P} =
\vector{g}_{P} - \vector{\gamma}_{P} \: .
\label{eq:gravity-disturbance-vector}
\end{equation}

Because the centrifugal parts of both the normal gravity vector
and the Earth's gravity vector are equal,
the gravity disturbance vector $\delta \vector{g}_{P}$
represents a purely gravitational effect.
As a consequence of the superposition principal \citep{blakely1996},
this effect is caused by contrasts between
the internal density distributions
of the actual Earth and the normal Earth.
In applied geophysics, these density differences are generally called
\textit{anomalous masses} \citep[e.g.,][]{hammer1945,lafehr1965},
\textit{density anomalies} \citep[e.g.,][]{forsberg1984},
or \textit{gravity sources} \citep[e.g.,][]{blakely1996}.
Here, we opted for using the last term.

The difference between the magnitudes of gravity vector
$g_{P} = \| \vector{g}_{P} \|$ and the normal gravity vector
$\gamma_{P} = \| \vector{\gamma}_{P} \|$, at the
same point $P$, is called \textit{gravity disturbance}
\citep{heiskanen-moritz1967, hofmann-wellenhof-moritz2005}
and can be represented as follows:

@@

Notice that the gravity disturbance $\delta g_{P}$ is not equivalent
to the magnitude of the gravity disturbance vector
$\delta \vector{g}_{P}$ \citep{barthelmes2013, sanso_sideris2013}.

On the other hand, the \textit{gravity anomaly vector} at $P$
is the difference between the gravity
vector at a point $Q^{\prime}$ on the Geoid (a particular
equipotential surface of the gravity potential) and the normal
gravity vector at a point $Q$ on the ellipsoid surface, both at the
same geodetic latitude and longitude (Fig. \ref{fig:surfaces}) as in
\begin{equation}
\Delta \vector{g}_{P} = \vector{g}_{Q^{\prime}} - \vector{\gamma}_{Q} .
\label{eq:gravity-anomaly-vector}
\end{equation}
Similarly to the gravity disturbance expression (eq.
\ref{eq:gravity-disturbance}), the gravity anomaly is given by
\begin{equation}
\Delta g_{P} = g_{Q^{\prime}} - \gamma_{Q} ,
\label{eq:gravity-anomaly}
\end{equation}
where $g_{Q^{\prime} } = \| \vector{g}_{Q^{\prime}} \|$ is
the magnitude of the gravity vector $\vector{g}_{Q}$ on the Geoid,
at $Q^{\prime}$, and $\gamma_{Q} = \| \vector{\gamma}_{Q} \|$ is the
magnitude of the normal gravity vector $\vector{\gamma}_{Q}$
on the reference ellipsoid, at the point $Q$ (Fig. \ref{fig:surfaces}).
As properly pointed out by \citet{barthelmes2013} the gravity anomaly,
by definition, depends on
longitude and latitude only and is not a function of height.
Because the gravity is on the Geoid and the normal gravity
is on reference ellipsoid, the gravity anomaly $\Delta g_{P}$
(eq. \ref{eq:gravity-anomaly}) is not a purely gravitational effect
due to the gravity sources, but rather a combination of gravitational
and centrifugal effects. Consequently, its upward continuation,
for example, could not be rigorously done.

@@

From eq. \ref{eq:gravity-disturbance-vector}, the gravity vector $\vector{g}_{i}$, at a point
$(x_{i}, y_{i}, z_{i})$ in the TCS (Fig. \ref{fig:TCS}a), can be represented by:
\begin{equation}
\vector{g}_{i} = \vector{\gamma}_{i} + \delta \vector{g}_{i} \: ,
\label{eq:gravity-vector-TCS}
\end{equation}
where $\vector{\gamma}_{i}$ and $\delta \vector{g}_{i}$
are, respectively, the normal gravity vector and the
gravity disturbance vector produced by the anomalous
masses at the point $(x_{i}, y_{i}, z_{i})$.

The gravity $g_{i}$ can be approximated by a first order Taylor's
expansion as follows \citep{sanso_sideris2013}:
\begin{equation}
g_{i} \approx \gamma_{i} +
\versor{\gamma}_{i}^{\top} \delta \vector{g}_{i} \: ,
\label{eq:gobs-approx}
\end{equation}
where $^{\top}$ denotes transposition,
$\versor{\gamma}_{i} = -\versor{u}_{i}$ is a unit
vector with the same direction as the normal gravity vector
$\vector{\gamma}_{i}$ at the point $(x_{i}, y_{i}, z_{i})$, in the
topocentric Cartesian coordinate system (Fig. \ref{fig:TCS}a), and
$\versor{u}_{i}$ is the unit vector $\versor{u}$
(eq. \ref{eq:unit-vectors}) evaluated at the corresponding
point $(h_{i}, \varphi_{i}, \lambda_{i})$ in the
GGS (Fig. \ref{fig:GCS-GGS}).
This approximation can be made because, fortunately,
the condition $\gamma_{i} \gg \| \delta \mathbf{g}_{i} \|$
is met at all points located above or on the Earth's surface.
This approximation is known in geodesy \citep[e.g.,][]{sanso_sideris2013}
and a similar approximation is largely used in applied geophysics
for representing total-field anomalies \citep[e.g.,][]{blakely1996}.
Notice that, in local- or regional-gravity studies, the unit
vector $\versor{\gamma}_{i}$ (eq. \ref{eq:gobs-approx})
may be considered constant throughout the study area and
parallel to the $z$ axis of the TCS (Fig. \ref{fig:TCS}a).
By using the approximation defined in eq.
\ref{eq:gobs-approx}, the gravity disturbance
(eq. \ref{eq:gravity-disturbance}) can be rewritten as
follows
\begin{equation}
\delta g_{i} \approx \versor{\gamma}_{P}^{\top} \delta \vector{g}_{i} \: ,
\label{eq:gravity-disturbance-approx-TCS}
\end{equation}
where $\versor{\gamma}_{P}$ represents the unit vector with
the same direction as the normal gravity vector $\vector{\gamma}_{P}$
at the origin $P$ of the TCS (Fig. \ref{fig:TCS}a).
This equation shows that the gravity disturbance $\delta g_{i}$ (eq. \ref{eq:gravity-disturbance}) is different from the magnitude
of the gravity disturbance vector $\delta \vector{g}_{i}$
produced by the gravity sources. Rather, it represents the
component of $\delta \vector{g}_{i}$ on the direction of the normal
gravity vector \citep{hofmann-wellenhof-moritz2005, sanso_sideris2013}.

@@

\begin{figure}
%    \vspace{5.5cm}
    \includegraphics{figures/cartesian-geodetic-systems.png}
    \caption{Schematic representation of the Geocentric Cartesian System (GCS) and the Geocentric Geodetic System (GGS). The GCS has the $Z$-axis coincident with the mean Earth's rotational axis,
    the $X$-axis pointing to the Greenwich meridian and the $Y$-axis
    directed so as to obtain a right-handed system. The GGS is      defined by an oblate ellipsoid with semi-minor axis $b$,
    coincident with the $Z$-axis of GCS, and a semi-major
    axis $a$. In this coordinate system, the position of a point is
    determined by the geometric height $h$, geodetic latitude
    $\varphi$ and longitude $\lambda$.
    The Earth's center of mass is represented
    by $O$, $P$ represents a point $(h_{P}, \varphi_{P}, \lambda_{P})$ and $P^{\prime}$ its projection onto the plane $XY$
    (Equatorial plane). The plane containing $O$, $P$ and
    $P^{\prime}$ is represented in gray in (a) and (b).
    The unit vectors $\versor{u}_{P}$, $\versor{v}_{P}$ and
    $\versor{w}_{P}$ define three mutually orthogonal
    directions at $P$ (eq. \ref{eq:unit-vectors}).
    In (b), $Q$ represents a point $(h_{Q}, \varphi_{Q}, \lambda_{Q})$,
    which is the projection of $P$ onto the reference ellipsoid, at
    the same latitude and longitude ($\varphi_{Q} = \varphi_{P}$ and $\lambda_{Q} = \lambda_{P}$).}
  \label{fig:GCS-GGS}
\end{figure}

\begin{figure}
    \includegraphics{figures/local-system.png}
    \caption{(a) Schematic representation of a topocentric Cartesian
    coordinate system (TCS) with origin at a point $P$. The axes $x$
    and $y$ are parallel to the unit vectors $\versor{v}_{P}$
    and $\versor{w}_{P}$ (eq. \ref{eq:unit-vectors} and
    Fig. \ref{fig:GCS-GGS}), respectively. On the other hand, the $z$ axis is opposite to the unit vector $\versor{u}_{P}$ (eq.
    \ref{eq:unit-vectors} and Fig. \ref{fig:GCS-GGS}) and points downward. The gray plane is the same shown in Fig. \ref{fig:GCS-GGS}.
    (b) Schematic representation of the gravity vector
    $\vector{g}_{P}$, normal gravity vector $\vector{\gamma}_{P}$,
    gravity disturbance vector $\delta \vector{g}_{P}$
    (eq. \ref{eq:gravity-disturbance-vector}) and unit vector
    $\versor{u}_{P}$ (eq. \ref{eq:unit-vectors}) at a point
    $P$.}
  \label{fig:TCS}
\end{figure}

\begin{figure}
    \includegraphics{figures/surfaces.png}
    \caption{Schematic representation of the gravity vector
        $\vector{g}_{P}$, normal gravity vector $\vector{\gamma}_{P}$,
        gravity disturbance vector $\delta \vector{g}_{P}$
        (eq. \ref{eq:gravity-disturbance-vector}), unit vector
        $\versor{u}_{P}$ (eq. \ref{eq:unit-vectors}) at a point $P$
        on the surface of the Earth, gravity vector $\vector{g}_{Q^{\prime}}$
        at a point $Q^{\prime}$ on the Geoid, normal gravity vector
        $\vector{\gamma}_{Q}$ at a point $Q$ on the reference ellipsoid,
        geometric height $h$, orthometric height $H$ and geoidal undulation
        $N$ \citep{heiskanen-moritz1967}.
        The dashed line passing through
        $Q$, $Q^{\prime}$ and $P$ is normal to the
        surface of the reference ellipsoid at $Q$. This figure
        shows a commonly used approximation in which the ellipsoid
        surface and the Geoid are represented as parallel surfaces,
        so that $h \approx H + N$.}
  \label{fig:surfaces}
\end{figure}
